### 2018-02-25 Sections/costs_and_attributes_in_quantum_networks.tex
Latin quote stubs
Crypto updated text
Very minor

@@

Analogous to the mutual information for classical systems is the \textit{coherent information} for quantum systems \cite{bib:PhysRevA.54.2629}, defined as,
\begin{align}\index{Coherent information}
I(\hat\rho,\mathcal{E}) = S(\mathcal{E}(\hat\rho)) - S_e(\hat\rho,\mathcal{E}).
\end{align}
\comment{Check up on this coherent information stuff!} Here $S_e$ is the \textit{exchange entropy}, a measure of how much information is exchanged between the state $\hat\rho$ and the environment under the action of the process. Specifically, it is given by the entropy of the environment subsystem in Eq.~(\ref{eq:proc_environment}), after application of the channel. This yields the intuitive interpretation that the coherent information is the information contained in the evolved state, discounted by the amount lost to the environment.

>>>>

\comment{Two cost vectors: max and min loss of information, provides upper and lower bounds}

@@

Analogous to the mutual information for classical systems is the \textit{coherent information} for quantum systems \cite{bib:PhysRevA.54.2629}, defined as,
\begin{align}\index{Coherent information}
I(\hat\rho,\mathcal{E}) = S(\mathcal{E}(\hat\rho)) - S_e(\hat\rho,\mathcal{E}).
\end{align}
Here $S_e$ is the \textit{exchange entropy}, a measure of how much information is exchanged between the state $\hat\rho$ and the environment under the action of the process. Specifically, it is given by the entropy of the environment subsystem in Eq.~(\ref{eq:proc_environment}), after application of the channel. This yields the intuitive interpretation that the coherent information is the information contained in the evolved state, discounted by the amount lost to the environment.

### 2018-02-25 Sections/cryptowars.tex
Very minor

%
% The Blockchain
%

\subsection{The Blockchain}\index{Blockchain}\index{Bitcoin}

@@

QKD is a relatively mature technology with already several commercial systems being available off-the-shelf\footnote{\cite{??? example companies}}. The main drawback is thus the ability to perform long-distance transmission of photons. Current QKD networks have been limited to relatively small distances, on the order of $\sim100$km, including in Austria, Switzerland, Japan, USA, and China \cite{bib:lo2014secure}. The longest distance QKD network that is currently planned is the Beijing to Shanghai QKD link, spanning a distance of $\sim2,000$km. This involves 32 trusted nodes\index{Trusted nodes} to break the full route into shorter segments.

Utilising space communications for the purpose of QKD has been discussed in several works \cite{bib:hughes2000quantum, bib:rarity2002ground, bib:pfennigbauer2003free, bib:aspelmeyer2003long, bib:armengol08}. As already demonstrated in space-based entanglement experiments \cite{bib:yin2017satellite, bib:ren2017ground, bib:liao2017satellite} far lower attenuation rates are possible than ground-only approaches. Since cryptography schemes such as BB84\index{BB84 protocol} do not require entanglement, these would appear to be the first widespread commercial application for quantum technologies.

The ready realisability of space based QKD was already noted in a variety of configurations including ground-to-space\index{Ground-to-space communication} and space-to-ground\index{Space-to-ground communication} quantum communication \cite{bib:rarity2002ground, bib:aspelmeyer2003long}. In the context of security, the first long-distance experiments that are likely to be demonstrated will employ trusted nodes\index{Trusted nodes}. For example, after performing QKD between satellite\index{Satellites} and ground stations\index{Ground stations}, a satellite could store the key for some time in a quantum memory\index{Quantum memory} until another QKD can be performed to another ground station using a one-time pad\index{One-time pad cipher} \cite{bib:liao2017satellite}. These types of experiments are currently planned to eventually facilitate intercontinental QKD\index{Intercontinental QKD} between China and Austria.

QKD has been widely experimentally demonstrated over long distances \cite{bib:Muller96}, and unlike quantum computing, QKD is at the stage of commercial viability. Thus, a quantum internet with low cost metrics would already find substantial utility with today's technology. Currently, great progress in being made in the implementation of QKD in fibre \cite{???}, over free-space \cite{bib:Buttler00}, and even over intercontinental satellite uplinks \cite{JWP}. It seems extremely likely that some government agencies would be rolling out QKD systems \cite{bib:Secret}, especially in light of the paranoia surrounding quantum codebreaking.

@@

The first described QKD scheme was the \textit{BB84} \cite{bib:BennetBrassard84}\index{BB84 protocol} protocol, which exploits the fact that states encoded in the 0/1-basis but measured in the $\pm$-basis (and vice versa) collapse randomly, yielding completely random measurement outcomes, whereas states measured in the same basis in which they were encoded always correctly communicate a single bit of information.

@@

\begin{table}[!htb]
\fbox{\parbox{0.965\columnwidth}{\texttt{ 
function BB84():
\begin{enumerate}
\item Alice chooses a random bit, $0$ or $1$.
\item Alice randomly chooses a basis, $\hat{X}$ or $\hat{Z}$.
\item Depending on the choice of basis, she encodes her bit into the polarisation of a single photon as:
\begin{align}
\ket{0}_Z &\equiv \ket{H}, \nonumber \\
\ket{1}_Z &\equiv \ket{V},
\end{align}
or,
\begin{align}
\ket{0}_X &\equiv \frac{1}{\sqrt{2}}(\ket{H}+\ket{V}), \nonumber \\
\ket{1}_X &\equiv \frac{1}{\sqrt{2}}(\ket{H}-\ket{V}).
\end{align}
\item Encoding into the randomly chosen basis, she transmits the randomly chosen bit to Bob.
\item She does not announce the choice of bit or basis.
\item Bob measures the bit in a randomly chosen basis, $\hat{X}$ or $\hat{Z}$.
\item The above is repeated many times.
\item Upon receipt of all qubits, Alice (publicly) announces the basis used for encoding each bit sent.
\item Qubits where Bob measured in the opposite basis to which Alice encoded are discarded, as they will be decorrelated from Alice.
\item The remaining measurement outcomes are guaranteed to yield identical bits between Alice and Bob.
\item Remaining is roughly half as many bits as were sent, which are random, but guaranteed to be identical between Alice and Bob.
\item Alice and Bob sacrifice some of their bits by publicly communicating them to check for consistency. This rules out intercept-resend attacks.
\item Privacy amplification may be used to distill the partially compromised key into a shorter but more secret one.
\end{enumerate}}}}
\caption{BB84\index{BB84 protocol} QKD protocol using polarisation-encoded\index{Polarisation encoding} photons. Upon completion of the protocol, Alice and Bob share a random bit-string.\index{One-time pad cipher}}\label{alg:bb84}
\end{table}

@@

E91 is slightly different to BB84. Here Alice and Bob share an entangled Bell-pair provided by a central authority. Then both Alice \textit{and} Bob measure their qubits in random bases. As with BB84, after measuring all qubits, they compare their choices of random bases. When they coincide, they have a shared, random bit. When they don't, they discard their result. From here the remainder of the protocol is the same as for BB84.

\comment{Explain E91 in detail}

>>>>

%
% Bitcoin & The Blockchain
%

\subsection{Bitcoin \& the Blockchain}\index{Blockchain}\index{Bitcoin}

\comment{To do}
\cite{bib:TomamichelBlockchain}

@@

QKD is a relatively mature technology with already several commercial systems being available off-the-shelf\footnote{\cite{??? example companies}} and initial space-based implementations have been successfully demonstrated \cite{Pan}.

@@

The first described QKD scheme was the \textit{BB84} \cite{bib:BennetBrassard84}\index{BB84 protocol} protocol, which exploits the fact that states encoded in the $\hat{Z}$-basis but measured in the $\hat{X}$-basis (and vice versa) collapse randomly, yielding completely random measurement outcomes, whereas states measured in the same basis in which they were encoded always correctly communicate a single bit of information.

@@

\begin{table}[!htb]
\fbox{\parbox{0.965\columnwidth}{\texttt{ 
function BB84():
\begin{enumerate}
\item Alice chooses a random bit, $0$ or $1$.
\item Alice randomly chooses a basis, $\hat{X}$ or $\hat{Z}$.
\item Depending on the choice of basis, she encodes her bit into the polarisation of a single photon as:
\begin{align}
\ket{0}_Z &\equiv \ket{H}, \nonumber \\
\ket{1}_Z &\equiv \ket{V},
\end{align}
or,
\begin{align}
\ket{0}_X &\equiv \frac{1}{\sqrt{2}}(\ket{H}+\ket{V}), \nonumber \\
\ket{1}_X &\equiv \frac{1}{\sqrt{2}}(\ket{H}-\ket{V}).
\end{align}
\item Encoding into the randomly chosen basis, she transmits the randomly chosen bit to Bob.
\item She does not announce the choice of bit or basis.
\item Bob measures the bit in a randomly chosen basis, $\hat{X}$ or $\hat{Z}$.
\item The above is repeated many times.
\item Upon receipt of all qubits, Alice (publicly) announces the basis used for encoding each bit sent.
\item Qubits where Bob measured in the opposite basis to which Alice encoded are discarded, as they will be decorrelated from Alice.
\item The remaining measurement outcomes are guaranteed to yield identical bits between Alice and Bob.
\item Remaining is roughly half as many bits as were sent, which are random, but guaranteed to be identical between Alice and Bob.
\item Alice and Bob sacrifice some of their bits by publicly communicating them to check for consistency. This rules out intercept-resend attacks.
\item Privacy amplification may be used to distill the partially compromised key into a shorter but more secret one.
\end{enumerate}}}}
\caption{BB84\index{BB84 protocol} QKD protocol using polarisation-encoded\index{Polarisation encoding} photons. Upon completion of the protocol, Alice and Bob share a random bit-string for use in a one-time-pad cipher\index{One-time pad cipher}.}\label{alg:bb84}
\end{table}

@@

E91 is slightly different to BB84. Here Alice and Bob share an entangled Bell-pair provided by a central authority. Then both Alice \textit{and} Bob measure their qubits in random bases. As with BB84, after measuring all qubits, they compare their choices of random bases. When they coincide, they have a shared, random bit. When they don't, they discard their result. From here the remainder of the protocol is the same as for BB84. Thre protocol is summarised in Alg.~\ref{alg:e91}.

\begin{table}[!htb]
\fbox{\parbox{0.965\columnwidth}{\texttt{ 
function E91():
\begin{enumerate}
\item A central server shares a Bell-pair between Alice and Bob,
\begin{align}
\ket{\Phi^+} = \frac{1}{\sqrt{2}}(\ket{0}_A\ket{0}_B+\ket{1}_A\ket{1}_B).
\end{align}
\item Alice randomly measures her qubit in either the $\hat{X}$ or $\hat{Z}$ basis.
\item Bob randomly measures his qubit in either the $\hat{X}$ or $\hat{Z}$ basis.
\item Alice and Bob share what their measurement bases were (classically and unencrypted).
\item When Alice and Bob's bases were consistent they store the measurement outcomes as a shared random bit.
\item Alice and Bob sacrifice some of their bits by publicly communicating them to check for consistency. This rules out intercept-resend attacks.
\item Privacy amplification may be used to distill the partially compromised key into a shorter but more secret one.
\end{enumerate}}}}
\caption{E91\index{E91 protocol} QKD protocol using polarisation-encoded\index{Polarisation encoding} photonic Bell-pairs. Upon completion of the protocol, Alice and Bob share a random bit-string of ruse in a one-time-pad cipher\index{One-time pad cipher}.}\label{alg:e91}
\end{table}

### 2018-02-25 Sections/entanglement_the_ultimate_quantum_resource.tex
Very minor

In addition to entanglement distribution, entangling measurements, e.g Bell state projections (Sec.~\ref{sec:bell_proj}), may be used as a primitive for many protocols. This is effectively entangled state distribution in reverse\index{Distributed entangling measurements}, whereby two clients transmit states to a host, who performs a joint entangling measurement upon them. For example, in the modularised model for cluster state quantum computing, two adjacent but distant modules might transmit optical qubits to a satellite, which projects them into the Bell basis, thereby creating a link between the respective modules via entanglement swapping. This isn't as powerful as entangled state distribution, since it cannot be used for, for example, E91 QKD\index{E91 QKD}, but nonetheless remains a powerful primitive for many protocols.

>>>>

In addition to entanglement distribution, entangling measurements, e.g Bell state projections (Sec.~\ref{sec:bell_proj}), may be used as a primitive for many protocols. This is effectively entangled state distribution in reverse\index{Distributed entangling measurements}, whereby two clients transmit states to a host, who performs a joint entangling measurement upon them. For example, in the modularised model for cluster state quantum computing\index{Measurement-based quantum computing}, two adjacent but distant modules might transmit optical qubits to a satellite, which projects them into the Bell basis, thereby creating a link between the respective modules via entanglement swapping\index{Entanglement swapping}. This isn't as powerful as entangled state distribution, since it cannot be used for, for example, E91 QKD\index{E91 QKD}, but nonetheless remains a powerful primitive for many protocols.

### 2018-02-25 Sections/essay_the_quantum_singularity.tex
Very minor

Since there is positive computational leverage associated with quantum networking -- to \textit{all} participating parties, irrespective of size -- this creates a self-reinforcing economic quantum ecosystem, whereby all market participants are  increasingly incentivised to continue contributing to the network, exponentially enhancing its collective power, with ever increasing returns over time. We will have reached a point of self-reinforcing exponential growth, driven by market forces. Because of the exponential scaling in computational power, it only becomes rational to ever-increasingly invest into further expansion, as every new qubit enhances the network more than the last.

@@

Since quantum algorithms provide quadratic speedup to \textbf{NP}-complete problems, and hence many optimisation problems, it follows that the existing distributed quantum computer will be able to perform self-enhancement by improving network routing efficiency, resource allocation, and even the design of the next generation of quantum computers, compared to what could be achieved using classical scheduling and optimisation algorithms. This self-improvement will also be self-reinforcing -- as the quantum network becomes more powerful, its capacity for self-improvement will accelerate, at which point the self-enhancement becomes self-sustaining, without the need for human intervention or classical computers to guide the way.

>>>>

Since there is positive computational leverage associated with quantum networking -- to \textit{all} participating parties, irrespective of size -- this creates a self-reinforcing economic quantum ecosystem, whereby all market participants are  increasingly incentivised to continue contributing to the network, exponentially enhancing its collective power, with ever increasing returns over time for all. We will have reached a point of self-reinforcing exponential growth, driven by market forces. Because of the exponential scaling in computational power, it only becomes rational to ever-increasingly invest into further expansion, as every new qubit enhances the network more than the last.

@@

Since quantum algorithms provide quadratic speedup to \textbf{NP}-complete problems, and hence many optimisation problems, it follows that the existing distributed quantum computer will be able to perform self-enhancement by improving network routing efficiency, resource allocation, and even the design of the next generation of quantum computers, compared to what could be achieved using classical scheduling and optimisation algorithms.

This self-improvement will also be self-reinforcing -- as the quantum network becomes more powerful, its capacity for self-improvement will accelerate, at which point the self-enhancement becomes self-sustaining, without the need for human intervention or classical computers to guide the way.
